opXRD: Open Experimental Powder X-ray Diffraction Database

### 2024-11-26 chapters/02_existing_datasets.tex
Added more information can be found to footnotes

There is also much publicly available powder diffraction data uploaded to datasets on Zenodo. However, this data is split into disparate entries that typically only contain the work of a single research project. Additionally, extracting powder diffraction data at scale is hindered by the fact that the data is often given in plain text files in non-standardized formats, which are difficult to parse programmatically. Some major crystal structure databases, such as the ICSD, do not appear in the above list, as they do not include powder diffraction data. This is because most structure solutions are achieved through single-crystal diffraction rather than powder diffraction.

>>>>

There is also much publicly available powder diffraction data uploaded to datasets on Zenodo. However, this data is split into disparate entries that typically only contain the work of a single research project. Additionally, extracting powder diffraction data at scale is hindered by the fact that the data is often given in plain text files in non-standardized formats, which are difficult to parse programmatically. \\

Aside from the databases mentioned above, we have also investigated several other crystal structure resources in search of experimental powder diffraction data. Crystal structure resources that were investigated but not found to contain any appreciable amount of publicly available experimental powder diffraction data include the Inorganic Crystal Structure Database,\footnote{More information on the ICSD can be found under \url{https://icsd.products.fiz-karlsruhe.de/}.}   Cambridge Structural Database,\footnote{More information on the CCDC can be found under \url{https://www.ccdc.cam.ac.uk/structures/}.}  the Materials Project database,\footnote{More information on the Materials Project can be found under\url{https://next-gen.materialsproject.org/}.}  the Crystallographic and Crystallochemical Database\footnote{More information on the Crystallographic and Crystallochemical Database can be found under \url{https://database.iem.ac.ru/mincryst/index.php}.},  the Bilbao Incommensurate Crystal Structure Database,\footnote{More information on the Incommensurate Crystal Structure Database can be found under \url{https://www.cryst.ehu.eus/bincstrdb/search/}.}  the Mineralogy Database,\footnote{More information on the Mineralogy database can be found under \url{https://webmineral.com/}.} IUCr Raw data letters,\footnote{More information on the IUCr Raw Data letters can be found under \url{https://iucrdata.iucr.org/x/index.html}.} and U.S. Naval Research Laboratory Crystal Lattice-Structures,\footnote{More information on the Crystal Lattice-Structures database can be found under \url{https://www.atomic-scale-physics.de/lattice/}.} the Athena Mineral database \footnote{More information on the Athena Mineral database can be found under \url{https://athena.unige.ch/athena/mineral/mineral.html}.} and the Protein data bank. \footnote{More information on the Protein data bank can be found under \url{https://www.rcsb.org/}.} This is to be expected as most structure solutions are achieved through single-crystal diffraction rather than powder diffraction.\\
